\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{array}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
\usepackage[table,xcdraw]{xcolor}
\usepackage{tabularray}
\usepackage{float}
\usepackage[export]{adjustbox}
\usepackage{longtable}
\usepackage{tcolorbox}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\usepackage[table]{xcolor}
\usepackage{hyperref}

\geometry{a4paper, margin=0.6in} % Adjust margins if necessary

\title{\textbf{\underline{Credit Appraisal Note}}}
\date{}

\begin{document}

\maketitle

\section*{\underline{Company Profile}}

\begin{longtable}{|m{3cm}|p{14cm}|} % Adjusted column widths
    \hline
    \multirow{8}{*}{\parbox{3cm}{\centering \textbf{Introduction}}} &
    \begin{itemize}
    \renewcommand\labelitemi{--}
        
        \item Founded in 1986 Initially established as M/s Gujarat Industries.
        
        \item Incorporated in 1995 Became Meghmani Organics Limited.
        
        \item Manufacturing Facilities Operates 6 manufacturing units located in Gujarat.
        
        \item Product Range Specializes in Pigments and Agrochemicals.
        
        \item Global Standing Among the top 3 Phthalocyanine-based pigment producers worldwide.
        
        \item Domestic Ranking Among the top 10 pesticide producers in India.
        
        \item Pigment Products Produces green and blue pigments used in printing ink, plastic, paints, textiles, leather, and rubber.
        
        \item Pesticides Manufactures a variety of pesticides for both crop and non-crop applications, including insect control for wood preservation and food grain storage.
        
    \end{itemize} \\
    \hline
    \multirow{6}{*}{\parbox{3cm}{\centering \textbf{Core Products and Services}}} &
    \begin{itemize}
    \renewcommand\labelitemi{--}
        
        \item Pigments Manufacturing:   - Meghmani Organics Ltd (MOL) produces green and blue pigment products.   - These pigments are used in various industries including printing ink, plastic, paints, textiles, leather, and rubber. 
        
        \item Agrochemicals Production:   - The company manufactures a wide variety of pesticides for both crop and non-crop applications.   - These include insect control products used in wood preservation and food grain storage. 
        
        \item Crop Protection Chemicals:   - MOL produces technicals, intermediates, and formulations of crop protection chemicals.   - Key products include insecticides, herbicides, and fungicides.   - Important intermediates are cypermethrin acid chloride, meta phenoxy benzaldehyde, and meta phenoxy benzyl alcohol. 
        
        \item Manufacturing Facilities:   - The company operates 6 manufacturing facilities located in Gujarat, India. 
        
        \item Market Position:   - Meghmani Organics is among the top 3 Phthalocyanine-based pigment players globally.   - It is also one of the top 10 producers of pesticides in India.
        
    \end{itemize} \\
    \hline
    \multirow{8}{*}{\parbox{3cm}{\centering \textbf{Primary Revenue}}} &
    \begin{itemize}
    \renewcommand\labelitemi{--}
        
        \item Pigments Manufacturing: Meghmani Organics Ltd produces green and blue pigment products used in various industries such as printing ink, plastic, paints, textiles, leather, and rubber.
        
        \item Agrochemicals Manufacturing: The company manufactures a wide variety of pesticides for crop and non-crop applications, including insect control in wood preservation and food grain storage.
        
        \item Crop Protection Chemicals: This segment includes the production and marketing of insecticides, herbicides, and fungicides, along with key intermediates like cypermethrin acid chloride, meta phenoxy benzaldehyde, and meta phenoxy benzyl alcohol.
        
    \end{itemize} \\
    \hline
    \multirow{8}{*}{\parbox{3cm}{\centering \textbf{Manufacturing Facilities}}} &
    \begin{itemize}
    \renewcommand\labelitemi{--}
        
        \item Founded in 1986 as M/s Gujarat Industries: The company was later incorporated in 1995 as Meghmani Organics Limited.
        
        \item Manufacturing Facilities: Meghmani Organics Ltd. operates 6 manufacturing facilities located in Gujarat.
        
        \item Product Range: The company manufactures pigments and agrochemicals, including green and blue pigment products used in printing ink, plastic, paints, textiles, leather, and rubber.
        
        \item Agrochemical Production: The company also produces a variety of pesticides for crop and non-crop applications, including insect control in wood preservation and food grain storage.
        
        \item Global and National Standing: Meghmani Organics is among the top 3 Phthalocyanine-based pigment players globally and among the top 10 producers of pesticides in India.
        
    \end{itemize} \\
    \hline
    \multirow{2}{*}{\parbox{3cm}{\centering \textbf{Corporate Offices}}} &
    \begin{itemize}
    \renewcommand\labelitemi{--}
        
        \item Corporate Office:   - Meghmani Organics Limited was founded in 1986 as M/s Gujarat Industries and incorporated in 1995.   - The company is headquartered in Gujarat, India. 
        
        \item Regional Offices:   - Meghmani Organics operates through 6 manufacturing facilities located in Gujarat, India.   - The company is a significant player in the global market, being among the top 3 Phthalocyanine-based pigment players in the world and among the top 10 producers of pesticides in India.
        
    \end{itemize} \\
    \hline
    \multirow{5}{*}{\parbox{3cm}{\centering \textbf{Research and Development}}} &
    \begin{itemize}
    \renewcommand\labelitemi{--}
        
        \item Company Overview Meghmani Organics Ltd was founded in 1986 as M/s Gujarat Industries and incorporated in 1995. It specializes in manufacturing pigments and agrochemicals.
        
        \item Manufacturing Facilities The company operates 6 manufacturing facilities located in Gujarat, India.
        
        \item Product Range Meghmani Organics Ltd produces green and blue pigment products used in various industries such as printing ink, plastic, paints, textiles, leather, and rubber. It also manufactures a wide variety of pesticides for crop and non-crop applications.
        
        \item Market Position The company is among the top 3 Phthalocyanine-based pigment players globally and one of the top 10 pesticide producers in India.
        
        \item Business Segments The company has significant operations in agrochemicals, including insecticides, herbicides, and fungicides.
        
        \item Financial Performance The company has faced challenges in recent quarters, including a decline in revenue and operational performance, leading to a downgrade in its CRISIL ratings.
        
        \item Research and Development Specific details about the research and development centers of Meghmani Organics Ltd are not provided in the given information.
        
    \end{itemize} \\
    \hline
\end{longtable}

\end{document}